---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

passwordrandom is an R package to interface to the PasswordRandom.com API - http://www.passwordrandom.com/api

The following functions are implemented:

- `random_chars`:	Generate random characters
- `random_doubles`:	Generate random doubles
- `random_guids`:	Generate random guids
- `random_ints`:	Generate random integers
- `random_passwords`:	Generate random passwords

The following data sets are included:

### News

- Version 0.0.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/passwordrandom")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(passwordrandom)

# current verison
packageVersion("passwordrandom")

random_chars()

random_doubles()

random_guids()

random_ints()

random_passwords()

```

### Test Results

```{r}
library(passwordrandom)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
